---
title: "Data-Product Assignment"
author: "Chandrasekar Ganesan"
date: "September 29, 2017"
output:
  slidy_presentation: default
  ioslides_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Overview

This is an R Markdown for Data-product week 4 assignment.
Purpose of the MTCars data set analyzer is to visually manipulate the mtcars data set via a dynamic web interface.

## Introduction 

 User can manipulate various attributes of the dataset and analyze the resulting plot visually

Following dimensions of the dataset can be manipulated dynamically

Attributes            | Attribute
----------------------|---------------------
Mile per gallon (mpg) | Quarter mile time (qsec)
Number of cylinders (cyl) | V/S (vs)
Diplacements (disp)   | Transmission type (am)
Real axle ratio (drat)| Gears (gear)
Weight (wt)           |


## Working model of Shiny app

Working model of the shiny app can be (found here)[https://gcsekar.shinyapps.io/MTCars-Analyser/].

## UI Code
```{r , echo = TRUE, eval=FALSE}
library(shiny)
library(ggplot2)

analyzeData <- mtcars
# Define UI for application that draws a histogram
shinyUI(pageWithSidebar(
  headerPanel("MTCars Data Analyzer"),
  sidebarPanel(
    
    sliderInput('sampleSize', 'Sample Size', min=10, max=nrow(analyzeData),
                value=nrow(analyzeData), step=5, round=0),
    
    selectInput('x', 'X', names(analyzeData),names(analyzeData)[1]),
    selectInput('y', 'Y', names(analyzeData), names(analyzeData)[6]),
    selectInput('color', 'Color', c('None', names(analyzeData)), names(analyzeData)[2]),
    
    checkboxInput('smooth', 'Smooth', value = 1),
    
    selectInput('facet_row', 'Facet Row', c(None='.', names(analyzeData))),
    selectInput('facet_col', 'Facet Column', c(None='.', names(analyzeData)))
  ),
  
  mainPanel(
    plotOutput('plot')
  )
))
```

## Server Code

```{r, echo=TRUE, eval=FALSE}
#
library(shiny)
library(ggplot2)

shinyServer(function(input, output) 
  dataset <- reactive( {
    mtcars[sample(nrow(mtcars), input$sampleSize),]
  })
  
  output$plot <- reactivePlot(function() {
    
    g <- ggplot(dataset(), aes_string(x=input$x, y=input$y)) + geom_point()
    
    if (input$color != 'None')
      g <- g + aes_string(color=input$color)
    
    facets <- paste(input$facet_row, '~', input$facet_col)
    if (facets != '. ~ .')
      g <- g + facet_grid(facets)
    
    if (input$smooth)
      g <- g + geom_smooth()
    
    g <- g + ggtitle("Analysis for MT Cars dataset", "(with Shiny)")
    print(g)
    
  }, height=600
  )
})
```

